\documentclass[../main.tex]{subfiles}
\begin{document}
\section{FAQ}

% \subsection{Most common errors}
\subsection{常见错误}

% For the moment, I'm basing myself on my own, because having changed syntax
% several times, I've made a number of mistakes. This section is going to be
% expanded.
目前，根据需要，已对语法进行了多次改进，这可能会带来很多错误，主要改进有：

\begin{itemize}\setlength{\itemsep}{10pt}
% \item \tkzcname{tkzDrawPoint(A,B)} when you need  \tkzcname{tkzDrawPoints}.
\item 绘制多个点时，\tkzcname{tkzDrawPoint(A,B)}命令中需要使用\tkzcname{tkzDrawPoints}命令。

% \item \tkzcname{tkzGetPoint(A)} When defining an object, use braces and not
% brackets, so write: \tkzcname{tkzGetPoint\{A\}}.
\item 使用\tkzcname{tkzGetPoint(A)}得到并命名一个点时，需要使用大括号而不是小括号，
因此，应该写成: \tkzcname{tkzGetPoint\{A\}}.

% \item \tkzcname{tkzGetPoint\{A\}} in place of \tkzcname{tkzGetFirstPoint\{A\}}.
% When a macro gives two points as results, either we retrieve these points using
% \tkzcname{tkzGetPoints\{A\}\{B\}}, or we retrieve only one of the two points,
% using \tkzcname{tkzGetFirstPoint\{A\}} or
% \tkzcname{tkzGetSecondPoint\{A\}}. These two points can be used with the
% reference \tkzname{tkzFirstPointResult} or
% \tkzname{tkzSecondPointResult}. It is possible that a third point is given as
% \tkzname{tkzPointResult}.
\item 可以用\tkzcname{tkzGetPoint\{A\}}命令代替\tkzcname{tkzGetFirstPoint\{A\}}命令。
当返回两个点时，可以使用\tkzcname{tkzGetPoints\{A\}\{B\}}命令一次得到两个点，
也可以使用\tkzcname{tkzGetFirstPoint\{A\}}命令或\tkzcname{tkzGetSecondPoint\{A\}}命令
分别得到两个点。
也可以通过\tkzcname{tkzFirstPointResult}命令或\tkzcname{tkzSecondPointResult}命令
引用这两个点中的一个点。
第3个点可以用\tkzcname{tkzPointResult}命令得到。

% \item \tkzcname{tkzDrawSegment(A,B A,C)} when you need
% \tkzcname{tkzDrawSegments}. It is possible to use only the versions with an "s"
% but it is less efficient!
\item 需要绘制多条线段时，应该使用\tkzcname{tkzDrawSegments}带\enquote{s}的命令，
而不能使用\tkzcname{tkzDrawSegment(A,B A,C)}命令，但注意该命令效率不高。

% \item Mixing options and arguments; all macros that use a circle need to know
% the radius of the circle. If the radius is given by a measure then the option
% includes a \tkzname{R}.
\item 命令选项与参数需要配合使用，所有圆相关的命令都需要知道圆的半径，
如果半径需要通过计算得到，则需要使用\tkzname{R}命令选项。

% \item \tkzcname{tkzDrawSegments[color = gray,style=dashed]\{B,B' C,C'\}} is a
% mistake. Only macros that define an object use braces.
\item \tkzcname{tkzDrawSegments[color = gray,style=dashed]\{B,B' C,C'\}}是错误语法，
只有对象定义命令才使用大括号。

% \item The angles are given in degrees, more rarely in radians.
\item 角度的度量单位常用度，极少使用弧度.
% \item If an error occurs in a calculation when passing parameters, then it is
% better to make these calculations before calling the macro.
\item 如果传入参数时需要计算，并发生了错误，那么建议在使用该命令前完成计算。

% \item Do not mix the syntax of \tkzNamePack{pgfmath} and \tkzNamePack{xfp}. I've
% often chosen \tkzNamePack{xfp} but if you prefer pgfmath then do your
% calculations before passing parameters.
\item 不要混合使用\tkzNamePack{pgfmath}和\tkzNamePack{xfp}的语法，
本宏包主要使用\tkzNamePack{xfp}语法，但如果更喜欢pgfmath库的语法，
则建议在传入参数前完成计算。

% \item Use of \tkzcname{tkzClip}: In order to get accurate results, I avoided
% using normalized vectors. The advantage of normalization is to control the
% dimension of the manipulated objects, the disadvantage is that with TeX, this
% implies inaccuracies. These inaccuracies are often small, in the order of a
% thousandth, but they lead to disasters if the drawing is enlarged. Not
% normalizing implies that some points are far away from the working area and
% \tkzcname{tkzClip} allows you to reduce the size of the drawing.
\item 有关\tkzcname{tkzClip}的用法: 为了得到更为精确的结果，
该宏包尽量避免向量归一化计算。向量归一化的优点是能够更好的控制对象尺寸，但其缺点
是在使用\TeX{}计算时，会带来精度损失。这些误差通常很小，约为千分之一，
但是当图幅较大时，其累积误差可能会导致灾难。
不归一化，意味着某些点可能会远离工作区域，可以使用\tkzcname{tkzClip}命令进行图形裁剪。

% \item An error occurs if you use the macro \tkzcname{tkzDrawAngle}
%  with too small an angle. The error is produced by the \NameLib{decoration}
% library when you want to place a mark on an arc. Even if the mark is absent, the
% error is still present. It is possible to get around this difficulty with the
% option \tkzname{mkpos=.2} for example, which will place the mark before the arc.
% Another possibility is to use the macro \tkzcname{tkzFillAngle}.
\item 如果角度太小时，使用\tkzcname{tkzDrawAngle}命令，则会发生错误。
该错误是使用在圆弧上放置标记的\NameLib{decoration}装饰库而产生的，
即使没有标记，该错误仍然存在。
可以使用mkpos=.2选项避免该错误，该选项能够在绘制圆弧之前布置标记。
另一种方法是使用\tkzcname{tkzFillAngle}命令避免该错误发生。

\end{itemize}

\end{document}
\endinput
